Databrary: Enabling sharing and reuse of research video data

### 2015-01-30 jcdl-15/paper.tex
Tweak footnotes and title

\title{Databrary: A digital data library for sharing research video}

@@

Research data repositories require a balance between generality and specificity.
General purpose repositories permit unstructured storage of arbitrary files (e.g. Dataverse\footnote{http://dataverse.org/}, Dryad\footnote{http://datadryad.org/}, and PURR\footnote{https://purr.purdue.edu/}), while those with rigorously structured schema require contributions to be to carefully formatted (e.g. Human Connectome Project\footnote{http://www.humanconnectomeproject.org}, Personal Genome Project\footnote{http://www.personalgenomes.org}, and TalkBank\footnote{http://talkbank.org/}).
The flexibility of general-purpose repositories make them especially well-suited to capture and archive entire datasets, but these systems do not facilitate search, understanding, or reuse without extensive, usually labor-intensive, curation to summarize or extract metadata \cite{Peer_2012}.
Targeted repositories, on the other hand, generate large-scale, homogeneous data sources that facilitate meta- and re-analysis, but are limited to specific research questions, losing the full richness, context, and innovation of the source materials and field.

>>>>

\title{Databrary: Enabling sharing and reuse of research video data}

@@

Research data repositories require a balance between generality and specificity.
General purpose repositories permit unstructured storage of arbitrary files (e.g., Dataverse\footnote{http://dataverse.org/}, Dryad\footnote{http://datadryad.org/}, PURR\footnote{https://purr.purdue.edu/}), while those with rigorously structured schema require contributions to be to carefully formatted (e.g., Human Connectome Project\footnote{http://www.humanconnectomeproject.org/}, Personal Genome Project\footnote{http://www.personalgenomes.org/}, TalkBank\footnote{http://talkbank.org/}).
The flexibility of general-purpose repositories make them especially well-suited to capture and archive entire datasets, but these systems do not facilitate search, understanding, or reuse without extensive, usually labor-intensive, curation to summarize or extract metadata \cite{Peer_2012}.
Targeted repositories, on the other hand, generate large-scale, homogeneous data sources that facilitate meta- and re-analysis, but are limited to specific research questions, losing the full richness, context, and innovation of the source materials and field.
